On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit

### 2023-01-10 manuscript/manuscript.tex
correction to KS stat scale
new method in section 3

Nonparametric bootstrap can also be used to approximate the null distribution
of the testing statistic with the bias correction from \citet{babu2004goodness}:
\begin{enumerate}
\item
  Draw a random sample $X_1^*,...,X_n^*$ from the empirical distribution $F_n$
  with replacement
\item
  Fit $F_\theta$ to the sample and obtain estimate $\hat\theta_n^*$ of $\theta$.
\item
  Obtain the empirical distribution function of the random sample $F_n^*$
\item
  Calculate bootstrap KS statistic
  \[
    D^* = \sup_x | F_n^* (x)- F_{\hat\theta_n}^*(x) - B_n(x) |.
  \]
  where $B_{n}(x) = \sqrt{n}(F_{n}(x) - F_{\hat\theta_n}(x))$ is the known
  bias term \citep{babu2004goodness}
\item
  Repeat the previous steps a large number $B$ times and use the empirical
  distribution of $D^*$ to approximate the null distribution of the observed
  statistic.
\end{enumerate}
The p-value of $D_n$ is, again, approximated by the proportion of $D_n^*$'s that
are greater than or equal to~$D_n$.

@@

When the observed data $X_1, \ldots, X_n$ are not independent but serially
dependent, the null distribution of the KS statistic $D_n$
in~\eqref{eq:ks_standard} changes. For a
stationary series, it may still be of interest to test whether the data come
from a completely specified distribution~$F$. When the serial dependence is
positive, the effective sample size is less than~$n$. The testing statistic
would be stochastically greater than that obtained from independent data, making
it more likely to reject the null hypothesis than it should. So the test is
liberal. The reasoning is similar when the serial dependence is negative,
in which case, the test is conservative.

@@

A complete remedy for the KS tests with serially dependent data is
challenging. The null distribution depends on the structure of the serial
dependence, which can be arbitrary in practice. A parametric bootstrap procedure
would need model specification of the dependence, whereas the primary interest
is to test the marginal distribution of the stationary series. A block
nonparametric bootstrap for stationary data \citep{kunsch1989jackknife} is
attempting, but the counterpart of a bias correction as in
\citet{babu2004goodness} is not available yet. Is there any approach that does
not require fully specification of the dependence of the stationary process
but still gives reasonably satisfactory correction to the size of the KS test in
certain applications?

We propose a semiparametric bootstrap procedure that assumes a working serial
dependence structure which does not need to be correctly specified. The working
serial dependence is introduced through copulas with the hope to approximate the
true serial dependence as allowed by the working copulas. A copula is a
multivariate distribution with standard uniform marginal distributions, which
completely characterizes the dependence structure of a multivariate
distribution \citep{hofert2018elements}. It separates the dependence structure
of a multivariate distribution from its marginal distributions. The normal copula
is the copula determined by the multivariate normal distribution. We propose to
use a normal working copula with an AR(1) structure to approximate the serial
dependence of the observations. Let $\hat\rho$ be the lag-1 sample auto
Spearman's rho of the observed data. A normal copula of dimension~$n$ can be
constructed with an AR(1) structure and its AR coefficient~$\psi$ is chosen to
ensure that the Spearman's rho matches $\hat\rho$. Let $\psi(\hat\rho)$ denote
this coefficient. The bootstrap procedure is as follows.
\begin{enumerate}
\item
  Generate $Z_1, \ldots, Z_n$ from an AR(1) process with autocorrelation
  coefficient $\psi(\hat\rho)$ such that the $Z_i$'s are $N(0, 1)$ variables.
\item
  Form a bootstrap sample $X_i^* = F^{-1} [\Phi(Z_i)]$,  $i = 1, \ldots, n$,
  where $\Phi$ is the distribution function of $N(0, 1)$.
\item
  Obtain the empirical distribution function $F_n^*$ of the bootstrap sample
  $X_1^*, \ldots, X_n^*$.
\item
  Calculate bootstrap KS statistic
  \[
    D^* = \sup_x \lvert F_n^* (x)- F(x) \rvert.
  \]
\item
  Repeat the previous steps a large number $B$ times and use the empirical
  distribution of the $B$ test statistics to approximate
  the null distribution of the observed statistic.
\end{enumerate}
The p-value of $D_n$ is, again, approximated by the proportion of $D_n^*$'s that
are greater than or equal to~$D_n$.

This process is semiparametric because the marginal distribution is
parametrically specified while the dependence structure of the stationary series
is only approximated. The closer the approximation is to the truth, the better
performance of the size of the KS test  If the true dependence is indeed a
normal copula with an AR(1) structure, this method is exact. When the true
dependence is not AR(1), it may still give a reasonable approximation that can
be useful for practical purposes. More complicated working models other
than the AR(1) process could be used, but we focus here on the AR(1) model.

@@

>>>>

Nonparametric bootstrap can also be used to approximate the null distribution
of the testing statistic with the bias correction from \citet{babu2004goodness}:
\begin{enumerate}
\item
  Draw a random sample $X_1^*,...,X_n^*$ from the empirical distribution $F_n$
  with replacement
\item
  Fit $F_\theta$ to the sample and obtain estimate $\hat\theta_n^*$ of $\theta$.
\item
  Obtain the empirical distribution function of the random sample $F_n^*$
\item
  Calculate bootstrap KS statistic
  \[
    D^* = \sup_x | \sqrt{n}\left(F_n^* (x)- F_{\hat\theta_n}^*(x)\right) - B_n(x) |.
  \]
  where $B_{n}(x) = \sqrt{n}(F_{n}(x) - F_{\hat\theta_n}(x))$ is the known
  bias term \citep{babu2004goodness}
\item
  Repeat the previous steps a large number $B$ times and use the empirical
  distribution of $D^*$ to approximate the null distribution of the observed
  statistic.
\end{enumerate}
The p-value of $D_n$ is, again, approximated by the proportion of $D_n^*$'s that
are greater than or equal to~$D_n$.

@@

Here we consider the situation where the observed data $X_1, \ldots, X_n$ are
not independent but serially dependent, and the hypothesized distribution $F$
contains no unknown parameters. The null distribution of the KS statistic $D_n$
in~\eqref{eq:ks_standard} changes with the serially dependence.
When the serial dependence is
positive, the effective sample size is less than~$n$. The testing statistic
would be stochastically greater than that obtained from independent data, making
it more likely to reject the null hypothesis than it should. So the test is
liberal. The reasoning is similar when the serial dependence is negative,
in which case, the test is conservative.

@@

A complete remedy for the KS tests with serially dependent data is
challenging. The null distribution depends on the structure of the serial
dependence, which can be arbitrary in practice. A parametric bootstrap procedure
would need specify a model for the dependence, whereas the primary interest
is to test the marginal distribution of the stationary series. A block
nonparametric bootstrap for stationary data \citep{kunsch1989jackknife} is
attempting, but the counterpart of a bias correction as in
\citet{babu2004goodness} is not available yet. Is there any approach that does
not require fully specification of the dependence of the stationary process
but still gives reasonably satisfactory correction to the size of the KS test in
certain applications?

We propose a semiparametric bootstrap procedure that assumes a working serial
dependence structure which does not need to be correctly specified. The working
serial dependence is introduced through copulas with the hope to approximate the
true serial dependence as allowed by the working copulas. A copula is a
multivariate distribution with standard uniform marginal distributions, which
completely characterizes the dependence structure of a multivariate
distribution \citep{hofert2018elements}. It separates the dependence structure
of a multivariate distribution from its marginal distributions. The normal copula
is the copula determined by the multivariate normal distribution. We propose to
use a normal working copula to approximate the serial
dependence of the observations.

The parameters of the working normal copula are
estimated from fitting an auto-regressive moving average (ARMA) model to the
observed data transformed to the standard normal scale. In particular, let
$Z_i = \Phi\{ F(X_i)\}$, $i = 1, \ldots, n$, where $\Phi$ is the distribution
function of the standard normal. Then we fit an ARMA$(p, q)$ model to
$Z_1, \ldots, Z_n$ with AR order $p$ and MA order $q$ selected by the Akaike
Information Criterion (AIC). This can be done with, for example, function
\texttt{auto.arima()} from  R package \texttt{forecast}
\citep{hyndman2008automatic}. Since it is known that the mean of $Z_i$'s are
zero, it is necessary to set the intercept of the ARMA model as zero in the
fitting process. The selected ARMA$(p, q)$ model with fitted
parameters will be used as the working model to generate bootstrap sample with
serial dependence mimicking that in the observed data. The unconditional
variance $\sigma^2$ of the ARMA model can be obtained with function
\texttt{tacvfARMA()} from R package \texttt{ltsa} \citep{mcleod2007algorithms}.

The semiparametric bootstrap procedure is as follows.
\begin{enumerate}
\item
  Generate $Z_1^*, \ldots, Z_n^*$ from the fitted ARMA$(p, q)$ process with
  innovation variance $1 / \sigma^2$ such that the $Z_i$'s are marginally
  standard normal variables.
\item
  Form a bootstrap sample $X_i^* = F^{-1} [\Phi(Z_i^*)]$,  $i = 1, \ldots, n$.
\item
  Obtain the empirical distribution function $F_n^*$ of the bootstrap sample
  $X_1^*, \ldots, X_n^*$.
\item
  Calculate bootstrap KS statistic
  \[
    D^* = \sup_x \lvert F_n^* (x)- F(x) \rvert.
  \]
\item
  Repeat the previous steps a large number $B$ times and use the empirical
  distribution of the $B$ test statistics to approximate
  the null distribution of the observed statistic.
\end{enumerate}
The p-value of $D_n$ is, again, approximated by the proportion of $D_n^*$'s that
are greater than or equal to~$D_n$.

This process is semiparametric because the marginal distribution is
parametrically specified while the dependence structure of the stationary series
is only approximated. The closer the approximation is to the truth, the better
performance of the size of the KS test, The dependence structure determined by
the working ARMA process approximates a wide class of dependence structures.
If the true dependence indeed has an ARMA structure, this method is exact. When
the true dependence is not covered the ARMA model, the working model may still
give a reasonable approximation that can
be useful for practical purposes.

@@

\jy{to be rewritten when the figures are generated.}
\jy{I suggest that we keep using gamma as the marginal distribution throughout.}
